Modeling Soot in Oxy-Coal Combustion Systems using Large Eddy Simulations

### 2020-01-14 manuscript/manuscript.tex
fixing manuscript for compilation: copied the original template and added current manuscript text.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[review,3p]{elsarticle}
%\documentclass[5p]{elsarticle}

\usepackage{url}
\usepackage{graphicx}
\usepackage{graphicx}
\usepackage{epic,eepic}
\usepackage{amsmath}
\usepackage{wasysym}
\usepackage{array}
\usepackage{color}
\usepackage[normalem]{ulem}         % for uline
\usepackage{wrapfig}
%\usepackage{textcomp}
\usepackage{outlines}
\usepackage{url}
\usepackage{array}
\usepackage{newtxtext,newtxmath}

\usepackage{biblatex}
\addbibresource{references.bib}
%======================================================================
\newcommand\tprime{\prime\prime\prime}
\newcommand{\prtl}[2]{\frac{\partial #1}{\partial #2}}
%======================================================================

@@

%====================================================================
\begin{abstract} % not to exceed 200 words
    Soot in coal combustion simulations is often ignored due to its computational complexity, despite its significant effect on flame temperature and radiation.  In this research, a 40 kW oxy-coal combustion system is modeled using Large Eddy Simulations (LES) and a detailed monodisperse coal soot model. Cases where soot is modeled are compared with cases where soot is neglected to determine the accuracy benefits and computational costs of modeling soot.

@@

@@

%====================================================================
\section{Introduction}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\documentclass[review,3p]{elsarticle}
%\documentclass[5p]{elsarticle}

\usepackage{graphicx}               % Include figure files
\usepackage{array}
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{bm}                     % bold math
\usepackage{caption}
\usepackage{subcaption}
\usepackage{lineno}
\usepackage[mathcal]{euscript}
\usepackage{xcolor}                  % coloring text

\usepackage{lipsum}

\newcommand{\prtl}[2]{\frac{\partial #1}{\partial #2}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{abstract}

Soot in coal combustion simulations is often ignored due to its computational complexity, despite its significant effect on flame temperature and radiation.  In this research, a 40 kW oxy-coal combustion system is modeled using Large Eddy Simulations (LES) and a detailed monodisperse coal soot model. Cases where soot is modeled are compared with cases where soot is neglected to determine the accuracy benefits and computational costs of modeling soot.

@@

%-----------------------------------------------------------------------------------

@@

\section{Introduction}

@@

%--------------------------------------------------------------------------------

@@
